Continuous Generalization of Buildings \\ by Growing and Aggregating

### 2017-09-19 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
added figures/ExperimentalComparison.pdf

Our goal scale is $1:50{,}000$.

\begin{figure}[tb]
	\centering
	\includegraphics{Data}
	\caption{Data.
		There are $2{,}590$ buildings, 
		which has $19{,}255$ edges in total.}
	\label{fig:Data}
\end{figure}

\begin{figure}[tb]
	\centering
	\includegraphics{GoalShape}
	\caption{Data for scale $1:15{,}000$.
		There are $2{,}590$ buildings, 
		which has $19{,}255$ edges in total.}
	\label{fig:GoalShape}
\end{figure}

\todo[inline]{comparison of simplification between Douglas--Peucker and 
	Imai--Iri}

>>>>

We set our goal scale at $1:50{,}000$ and $d_\mathrm{G}=25\,\mathrm{m}$
so that we can compare our result with the exiting data.
Also, this setting makes \eq\ref{eq:S_g} hold, 
where $M_\mathrm{g}=50{,}000$, $d_\mathrm{G}=25\,\mathrm{m}$, 
and $l=0.3\,\mathrm{mm}$.
In \eq\ref{eq:d_Dtmin}, the first part is always smaller than the second part 
according to our settings.
As a result $\dtrm{D}=t\cdot 35\,\mathrm{m}$, 
where $\dtrm{E}=t\cdot 7.5\,\mathrm{m}$ 
according to \eq\ref{eq:d_Et} and $\alpha=1.5$.

Our program took $93.6\,\mathrm{s}$ 
to compute the goal shapes of the built-up areas.
\fig\ref{fig:GoalShape} shows the bridged buildings and the goal shapes.
In \fig\ref{fig:GoalShape}b,
the $56$ built-up areas have $2{,}095$ edges before line simplification.
Using the Imai--Iri algorithm, we have $1{,}102$ edges left.
In comparison, there are $1{,}597$ edges left if we simplify using
the Douglas--Peucker algorithm.

\begin{figure}[tb]
	\centering
	\includegraphics{Data}
	\caption{Data.
		There are $2{,}590$ buildings, 
		which have $19{,}255$ edges in total.}
	\label{fig:Data}
\end{figure}

\begin{figure}[tb]
	\centering
	\includegraphics{GoalShape}
	\caption{Some results for time $t=1$, at scale $1:50{,}000$.
		(a) Bridged buildings.
		(b) Goal shapes of the built-up areas, without removing small holes.
		There are $56$ built-up areas, which have $1{,}102$ edges in total.
	}
	\label{fig:GoalShape}
\end{figure}

\begin{figure}[tb]
	\centering
	\includegraphics{ExperimentalComparison}
	\caption{.
	}
	\label{fig:ExperimentalComparison}
\end{figure}
